Evaluating Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe using radiocarbon data

### 2019-05-26 article/05_Conclusion.Rmd
spelling

1. Replacing time slices in the correlation analysis by a moving window approach to get a contious interaction proxy time series.

@@

3. Comparing the real world correlation time series with ones constructed from simulated, randomly permutating observations to test the significance of seemingly positive or negative correlation.

>>>>

1. Replacing time slices in the correlation analysis by a moving window approach to get a continuous interaction proxy time series.

@@

3. Comparing the real world correlation time series with ones constructed from simulated, randomly permuting observations to test the significance of seemingly positive or negative correlation.
